---
output: github_document
prefer-html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# akairmonitorr

<!-- badges: start -->
<!-- badges: end -->

Package for the AMQA data management team.
Contains functions for the common data cleaning & wrangling steps the team 
comes across.

## Installation

You can install the development version of akairmonitor from [GitHub](https://github.com/simeon-s-ng/akairmonitorr) with:

```{r eval=FALSE}
# install.packages("pak")
pak::pak("simeon-s-ng/akairmonitorr")

# OR

# install.packages("devtools")
devtools::install_github("simeon-s-ng/akairmonitorr")
```

## Example

```{r load example}
library(akairmonitorr)
```

You can query our internal AirVision server for data with:

```{r query agileweb, eval=FALSE}
key <- API_KEY
quant_460 <- query_agileweb("Quant_MOD00460", "PM25", start = "2024-05-13T00:00:00", key) |>
  clean_pm25()
```

NOTE: To obtain an AirVision API key, you may request a key by reaching out to the AMQA Data Management Team at [amqa-data-request@alaska.gov](mailto:amqa-data-request@alaska.gov)

Or read a .csv basic data export from AirVision:

```{r read aa}
file_path <- "C:/Data Analysis/Testing/data/haines_quant.csv"
haines_quant <- read_aa(file_path)

head(haines_quant)
```

You can create an OpenAir diurnal plot with your imported data (must follow openair package column naming conventions):

```{r plot quant pm25, fig.width=10, fig.height=10}
# plot_quant_pm25(haines_quant, "Haines")
```

You can create an OpenAir wind rose with your imported data (must follow openair package column naming conventions):

```{r}
# plot_wind_rose(data, "Hourly Wind Speed (m/s) vs. Direction at the A Street Monitor 2021")
```
